---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



[![Build Status](https://travis-ci.org/kota7/combiter.svg?branch=master)](https://travis-ci.org/kota7/combiter)
[![CRAN Status](http://www.r-pkg.org/badges/version/combiter)](http://www.r-pkg.org/badges/version/combiter)
[![](http://cranlogs.r-pkg.org/badges/combiter)](http://cran.rstudio.com/web/packages/combiter/index.html)

# combiter: Combinatorics Iterators for R

This package provides iterators for combinations, permutations, subsets, and cartesian product, with which one can go through the elements without creating a huge set of
all possible values.

Since `v1.0.2`, the iterator objects of the package inherit the `iter` class from [iterators](https://cran.r-project.org/web/packages/iterators/index.html) package.
As a result, the objects are also compatible with [foreach](https://cran.r-project.org/web/packages/foreach/index.html) library.


## Installation and import

Install from CRAN by:
```{r, eval=FALSE}
install.packages("combiter")
```

Or install development version by:
```{r, eval=FALSE}
devtools::install_github("kota7/combiter")
```

Use by
```{r}
library(combiter)
```


## Usage

Please visit the [Documentation Page](https://kota7.github.io/combiter) for the package introduction.
