---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



[![Build Status](https://travis-ci.org/kota7/combiter.svg?branch=master)](https://travis-ci.org/kota7/combiter)
[![CRAN Status](http://www.r-pkg.org/badges/version/combiter)](http://www.r-pkg.org/badges/version/combiter)


# combiter: Combinatorics Iterators for R

This package provides iterators for combinations, permutations, and subsets,
which allow you to go through all elements without creating a huge set of
all possible values.


## Installation and import

Install by

```{r, eval=FALSE}
devtools::install_github("kota7/combiter")
```

Use by
```{r}
library(combiter)
```


## Overview

This package provides three classes of iterator objects: `iperm`, `icomb`, and `isubset`. 

- `iperm(n)` goes through all permutation of integers 1 to `n`.
- `icomb(n, k)` goes through all combinations of `k` integers out of 1 to `n`.
- `isubset(n)` goes through all subsets of integers 1 to `n`.

The iterators do not store all possible values inside the object. 
Instead, they compute the next or previous element on spot.
This implementation would be more memory efficient with a large `n`, 
since the number of possible cases grows exponentially or even faster for these
Combinatorics operations.

## Examples

```{r}
x <- iperm(3)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```

```{r}
x <- icomb(5, 3)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```

```{r}
x <- isubset(3)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```
