---
title: "combiter: Combinatorics Iterators for R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


[![Build Status](https://travis-ci.org/kota7/combiter.svg?branch=master)](https://travis-ci.org/kota7/combiter)
[![CRAN Status](http://www.r-pkg.org/badges/version/combiter)](http://www.r-pkg.org/badges/version/combiter)
[![](http://cranlogs.r-pkg.org/badges/combiter)](http://cran.rstudio.com/web/packages/combiter/index.html)





## Overview

This package provides iterators for combinations, permutations, subsets, and cartesian product, with which one can go through the elements without creating a huge set of
all possible values.

Since `v1.0.2`, the iterator objects of the package inherit the `iter` class from [iterators](https://cran.r-project.org/web/packages/iterators/index.html) package.
As a result, the objects are also compatible with [foreach](https://cran.r-project.org/web/packages/foreach/index.html) library.



## Installation and Import

Install from CRAN:
```{r, eval=FALSE}
install.packages("combiter")
```

Install development version:
```{r, eval=FALSE}
devtools::install_github("kota7/combiter")
```

Import:
```{r}
library(combiter)
```



## Basic Iterators

This package provides four iterator classes for integer vectors: `icomb`, `iperm`, `isubset`, and `icartes`. 

- `icomb(n, k)` goes through all combinations of k integers out of `1` to `n`.
- `iperm(n, k)` goes through all permutations of size `k` consisting of integers `1` to `n` of size `k`.
- `isubset(n)` goes through all subsets of integers `1` to `n`.
- `icartes(c(n1, n2, ...))`, available for `v1.0.2+`, goes through cartesian products of `1` to `n1`, `1` to `n2` ....


The iterators do not store all possible values inside the object. 
Instead, they compute the next or previous element on spot.
This implementation would be more memory efficient with a large `n`, 
since the number of possible cases grows exponentially or even faster for these
Combinatorics operations.


### Examples

```{r}
x <- icomb(5, 3)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```

```{r}
x <- iperm(4, 2)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```

```{r}
x <- isubset(3)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```

```{r}
x <- icartes(c(3, 4))
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```



## Iterate through Values (v1.0.2+)

Each iterator shown above has its `value` counterpart.
For example, `ipermv`, the value version of `iperm`, iterates through all permutations of `k` elements from `n` values.


```{r}
x <- ipermv(c("A", "G", "C"), 2)
ct <- 0
while (hasNext(x))
{
  ct <- ct + 1
  i <- nextElem(x)
  cat(sprintf("%3d : %s\n", ct, paste0(i, collapse = " ")))
}
```

`icombv`, `isubsetv`, and `icartesv` are also defined analogously.


## Use with `foreach` (v1.0.2+)

Since `v1.0.2`, the iterator objects can be used with `foreach` function from [foreach](https://cran.r-project.org/web/packages/foreach/index.html).

```{r}
library(foreach)
foreach(i = icomb(3, 2)) %do% sum(i)
```


## Links

- [combiter (GitHub repository)](https://github.com/kota7/combiter)



